SunPy - Python for Solar Physics

### 2014-01-24 2-1-Map.tex
Added bg for listing in main and map files, plus few typos fixed.  Also reorderd some sentence into s/c launch

\subsection{Map}
Map is a 2D spatial data type, primarily used for images of the Sun and 
inner heliosphere. It provides a wrapper around a data array (\texttt{numpy} 
\texttt{ndarray}) and gives easy access to standard meta data in the header of 
the image, via the \texttt{.meta} attribute as well as some convienience 
properties for more standard meta data, \textit{i.e.} \texttt{.instrument}, 
\texttt{.wavelength} or \texttt{.coordinate\_system}. Demonstrated in Listing 
\ref{code:aia_1} is this meta data parsing and `pretty printing' of the Map.
The \texttt{Map} object provides convenience methods for many functions 
such as, rotation and re-sampling as well as convenience visualisation 
functions, providing a easy to use as well as powerful interface.
Listing \ref{code:aia_1} also demonstrates the quick plot functionality of 
\texttt{Map}, see Section \ref{subsec:Viz} for more discussion of plotting.

The design of the map submodule is such that each instrument or 
detector can subclass the parent \texttt{GenericMap} class to implement 
special meta data handling or other data specific functions. Each subclass 
of \texttt{GenericMap} can register with the \texttt{Map} factory class and 
by implementing a method that returns \texttt{True} if the meta data 
matches meta data for that instrument or detector, the \texttt{Map} factory 
will automatically return an instance of the specific \texttt{GenericMap} 
subclass. As of version 0.4 SunPy has \texttt{Map} specialisations for the 
following instruments: \textit{IRIS} SJI frames, \textit{SDO/AIA} and 
\textit{HMI}, \textit{SOHO/EIT} and	\textit{LASCO}, \textit{STEREO/EUVI} and 
\textit{COR}, \textit{YOHKOH/SXT}, \textit{RHESSI}, \textit{PROBA2/SWAP} and 
\textit{HINODE/XRT}.

@@

\begin{listing}[H]
\begin{minted}{pycon}

@@

>>> aia.peek()
\end{minted}
\includegraphics[width=0.8\columnwidth]{aia_map_example}
\caption{Demonstration of the \texttt{AIAMap} specilisation of 
\texttt{GenericMap}. The Map is created from a \textit{AIA} FITS file and the 
key meta data and array overview is printed. Then a quick view plot is created 
by using the \texttt{.peek()} method.}
\label{code:aia_1}
\end{listing}

As well as providing the base classes the map submodule provides two 
collection classes, \texttt{CompositeMap} and \texttt{MapCube}, for 
temporally and spatially aligned data respectively. \texttt{MapCube} 
provides methods for animation of its series of \texttt{Map} objects. 
\texttt{CompositeMap} provides methods for overlaying spatially aligned 
data, with support for visualisation of images and contour lines overlaid 
upon each other.

\begin{listing}[H]
\begin{minted}{python}
import matplotlib.pyplot as plt
import sunpy.map

@@

\begin{listing}[H]
\begin{minted}{python}
import sunpy.map

@@

\begin{listing}[h]
\begin{minted}{python}
import sunpy.map
from matplotlib import animation

>>>>

\subsection{Map}
Map is a 2D spatial data type, primarily used for images of the Sun and 
inner heliosphere. It provides a wrapper around a data array (\texttt{numpy} 
\texttt{ndarray}) and gives easy access to standard meta data in the header of 
the image, via the \texttt{.meta} attribute as well as some convenience 
properties for more standard meta data, \textit{i.e.} \texttt{.instrument}, 
\texttt{.wavelength} or \texttt{.coordinate\_system}. Demonstrated in Listing 
\ref{code:aia_1} is this meta data parsing and `pretty printing' of the Map.
The \texttt{Map} object provides convenience methods for many functions 
such as, rotation and re-sampling as well as convenience visualisation 
functions, providing an easy to use as well as powerful interface.
Listing \ref{code:aia_1} also demonstrates the quick plot functionality of 
\texttt{Map}, see Section \ref{subsec:Viz} for more discussion of plotting.

The design of the map submodule is such that each instrument or 
detector can subclass the parent \texttt{GenericMap} class to implement 
special meta data handling or other data specific functions. Each subclass 
of \texttt{GenericMap} can register with the \texttt{Map} factory class and 
by implementing a method that returns \texttt{True} if the meta data 
matches meta data for that instrument or detector, the \texttt{Map} factory 
will automatically return an instance of the specific \texttt{GenericMap} 
subclass. As of version 0.4 SunPy has \texttt{Map} specialisations for the 
following instruments: 
\textit{YOHKOH/SXT},\textit{SOHO/EIT} and \textit{LASCO}, \textit{RHESSI}, 
\textit{STEREO/EUVI} and \textit{COR}, \textit{HINODE/XRT},
\textit{PROBA2/SWAP}, \textit{SDO/AIA} and \textit{HMI}, 
and \textit{IRIS} SJI frames.

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}

@@

>>> aiamap.peek()
\end{minted}
\includegraphics[width=0.8\columnwidth]{aia_map_example}
\caption{Demonstration of the \texttt{AIAMap} specialisation of 
\texttt{GenericMap}. The Map is created from an \textit{AIA} FITS file and the 
key meta data and array overview is printed. Then a quick view plot is created 
by using the \texttt{.peek()} method.}
\label{code:aia_1}
\end{listing}

As well as providing the base classes the map submodule provides two 
collection classes, \texttt{CompositeMap} and \texttt{MapCube}, for 
temporally and spatially aligned data respectively.
\texttt{CompositeMap} provides methods for overlaying spatially aligned 
data, with support for visualisation of images and contour lines overlaid 
upon each other.
\texttt{MapCube} 
provides methods for animation of its series of \texttt{Map} objects. 
Listings~\ref{code:compmap_1} and \ref{code:mapcube_1} shows how to interact 
with these classes.
In addition, Listing~\ref{code:mapcube_2} demonstrates how the \texttt{MapCube} 
classes interacts with the \texttt{animation} module to save a video.

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{python}
import matplotlib.pyplot as plt
import sunpy.map

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{python}
import sunpy.map

@@

\begin{listing}[h]
\begin{minted}[bgcolor=bg]{python}
import sunpy.map
from matplotlib import animation
